\documentclass[12pt,a4paper,oneside]{article}

\usepackage[margin=3cm]{geometry}

\usepackage{hyperref}
\hypersetup{
    pdftitle={COM 421, 430, Software Engineering I, II},%
    pdfauthor={Toksaitov Dmitrii Alexandrovich},%
    pdfsubject={Syllabus},%
    pdfkeywords={COM;}{421;}{syllabus;}{software;}{engineering},%
    colorlinks,%
    linkcolor=black,%
    citecolor=black,%
    filecolor=black,%
    urlcolor=black
}

\newcommand{\R}[1]{\uppercase\expandafter{\romannumeral #1\relax}}

\begin{document}

    \title{COM 421, 430, Software Engineering \R{1}, \R{2}}
    \author{
        American University of Central Asia\\
        Software Engineering Department
    }
    \date{}
    \maketitle

    \section{Course Information}

        \begin{description}
            \item[Course IDs]\hfill\\
                COM 421, 3705\\
                COM 430, 3881
            \item[Course Repositories]\hfill\\
                \url{https://github.com/auca/com.421}\\
                \url{https://github.com/auca/com.430}
            \item[Place]\hfill\\
                AUCA new campus, room G30
            \item[Time]\hfill\\
                Monday 12:45\\
                Wednesday 12:45
        \end{description}

    \section{Prerequisites}

        COM 112, Programming \R{2}. Object Oriented Design and GUI Programming\\
        COM 324, Algorithm Analysis

        \section{Contact Information}

            \begin{description}
                \item[Instructor]\hfill\\
                    Toksaitov Dmitrii Alexandrovich\\
                    \href{mailto:toksaitov_d@auca.kg}{toksaitov\_d@auca.kg}
                \item[Office]\hfill\\
                    AUCA new campus, room 315
                \item[Office Hours]\hfill\\
                    \begin{itemize}
                        \item Monday 10:40--12:45
                        \item Wednesday 14:00--15:00
                    \end{itemize}
            \end{description}

    \section{Course Overview}

        The course introduces students to software engineering, teaching each of the individual steps of the software life cycle: requirements, design, coding, testing and software delivery. The course covers estimating man months to complete a project and writing project proposals. Along with the theory, students will go through all the stages of software development on their own projects. This is a two-semester course designed for Software Engineering majors and minors.

    \section{Topics Covered}

        \begin{itemize}
            \item Software Engineering Concepts
            \item Software Development Methodologies
            \item Agile Software Development
            \item Requirements Engineering
            \item System Design and Modeling
            \item System Implementation
            \item Software Testing
            \item Software Evolution
            \item Project Management
            \item Dependability and Security
        \end{itemize}

    \section{Practice Tasks}

        Students are required to finish 10 practice tasks. The tasks are based on topics discussed during lectures. Each task should be finished during the class to receive a grade.

    \section{Course Projects}

        The course contains two projects for each semester. Each project requires to develop a software product for an imaginary customer. Small teams of 4 students will compete to deliver solutions to a specified problem. Teams will go through all steps of software production such as requirements specification, software design, construction, testing, deployment, and maintenance.

    \section{Reading}

        Software Engineering (9'th Edition) by Ian Sommerville (AUCA Library Call Number: QA76.758.S657 2011, ISBN: 978-0137035151)

            \subsection{Supplemental Reading}

                \begin{enumerate}
                    \item The Mythical Man-Month: Essays on Software Engineering, Second Edition by Frederick P. Brooks Jr. (ISBN: 858-0001065793)
                    \item Code Complete: A Practical Handbook of Software Construction by Steve McConnell (AUCA Library Call Number: QA76.76.D47M39 2004, ISBN: 079-0145196705)
                    \item Design Patterns: Elements of Reusable Object-Oriented Software by Erich Gamma, Richard Helm, Ralph Johnson, John Vlissides (AUCA Library Call Number: QA 76.64 D47 1995, ISBN: 978-0201633610)
                    \item Refactoring: Improving the Design of Existing Code by Martin Fowler, Kent Beck, John Brant, William Opdyke, Don Roberts (AUCA Library Call Number: QA76.76.R42 F695 1999, ISBN: 978-0201485677)
                \end{enumerate}

    \section{Grading}

        \begin{itemize}
            \item Practice tasks (40\%)
            \item Course projects (several parts)
            \begin{itemize}
                \item Major part of the final grade (60\%)
            \end{itemize}
        \end{itemize}

        \begin{itemize} \itemsep-10pt \parskip0pt \parsep0pt
            \item[--] 90\%--100\%: A\\
            \item[--] 80\%--89\%: A-\\
            \item[--] 70\%--79\%: B+\\
            \item[--] 65\%--69\%: B\\
            \item[--] 60\%--64\%: B-\\
            \item[--] 56\%--59\%: C+\\
            \item[--] 53\%--55\%: C\\
            \item[--] 50\%--52\%: C-\\
            \item[--] 46\%--49\%: D+\\
            \item[--] 43\%--45\%: D\\
            \item[--] 40\%--42\%: D-\\
            \item[--] Less than 39\%: F
        \end{itemize}

    \section{Rules}

        Students are required to follow the rules of conduct of the Software Engineering Department and American University of Central Asia.

\end{document}
